\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{margin=1in}

\begin{document}

\begin{center}
  {\LARGE\bfseries Le Van Hoang}\\[5pt]
  {\large AI Engineer Intern}\\[5pt]
  (+84) 3 282 81624 \quad
  \href{mailto:22520465@gm.uit.edu.vn}{22520465@gm.uit.edu.vn} \quad
  \href{https://www.linkedin.com/in/hoanglvuit}{linkedin.com/in/hoanglvuit} \quad
  \href{https://github.com/hoanglvuit}{github.com/hoanglvuit}
\end{center}

\section*{Summary}
An AI/Machine Learning student with a strong foundation in Deep Learning (DL), Machine Learning (ML) and experience conducting research on adversarial examples. Eager to gain hands-on experience through an internship in a real-world production environment. Highly motivated to learn, grow, and contribute to impactful projects.

\section*{Education}
\textbf{University of Information Technology (UIT)}, Ho Chi Minh City, Vietnam\\
Bachelor of Computer Science \hfill 09/2022--01/2026 (expected)\\
GPA: 8.95/10.0 (current)

\section*{Technical Skills}
\textbf{Languages:} Python, HTML, CSS\\
\textbf{ML \& Frameworks:} PyTorch, scikit-learn, Hugging Face, FastAPI\\
\textbf{Tools:} Git, Docker, CI/CD, Linux, Jenkins\\
\textbf{Skill:} MLOps

\section*{Projects}
\textbf{Chatbot about Vietnam criminal law QA} \hfill Solo Project, 05/2025--06/2025\\
\begin{itemize}[left=0pt]
  \item Developing a Vietnamese Criminal Law QA Chatbot using RAG architecture.
  \item Developed the backend with FastAPI and the frontend using Tailwind CSS and Vite.
  \item Deployed the frontend on Vercel (free-tier) and the backend on a VPS.
  \item Implemented CI/CD automation with Jenkins to build and push Docker images, SSH into the VPS, pull images, and run containers. Full deployment workflow documented on GitHub.
\end{itemize}

\textbf{Legal Document Retrieval -- Top 3 SoICT} \hfill Team Size: 4, 10/2025--12/2025\\
\begin{itemize}[left=0pt]
  \item Led team as main developer; built a legal document retrieval system integrating a Bi-Encoder model for retrieval and Cross-Encoder models for ranking.
  \item Fine-tuned the Bi-Encoder with Multi-Negative Ranking Loss and enhanced Cross-Encoder training via negative mining techniques.
\end{itemize}

\textbf{Drought Prediction Using Meteorological \& Soil Data} \hfill Team Size: 5, 03/2025--05/2025\\
\begin{itemize}[left=0pt]
  \item Researched and designed an AI architecture to forecast drought severity 7 weeks ahead using 175 days of historical weather data and regional soil features.
  \item Engineered temporal features (trends, seasonality, lags) and evaluated sequence models (RNN, GRU, LSTM, Transformer) for time-aware embeddings.
\end{itemize}

\textbf{Adversarial Patch Attacks on Sign Classifiers} \hfill Solo Project, 03/2025--05/2025\\
\begin{itemize}[left=0pt]
  \item Trained a CNN to classify traffic signs, achieving 95\% accuracy and 90\% F1 score.
  \item Applied the CamoPatch technique to deceive the classifier, reducing accuracy from 95\% to 1\%.
  \item Enhanced the genetic algorithm by customizing the individual update mechanism for real-world constraints.
\end{itemize}

\section*{Certifications}
Machine Learning Specialization and Deep Learning Specialization, Coursera -- Andrew Ng (2024)\\
Applications of AI for Anomaly Detection, NVIDIA (2025)\\
TOEIC: Listening \& Reading: 765 (2024), Speaking \& Writing: 280 (2024)

\section*{Research and Competitions}
SoICT Hackathon 2024: Top 3 -- Legal Document Retrieval\\
Home Credit -- Credit Risk Model Stability, Kaggle Competition: Top 80/3856 -- Silver medal\\
\textit{Optimizing Legal Document Retrieval in Vietnamese with Semi-Hard Negative Mining}: ICCCI 2025 (first author -- accepted)\\
\textit{Prompt Manipulation for Targeted Adversarial Object Generation in Stable Diffusion}: (first author -- manuscript ready for submission)

\end{document}